Learning filters from user provided image makers

### 2020-06-07 main.tex
testing new caption description

\begin{figure}[!t]
  \centering
  \subfloat[Groups of three classes centered on the origin.\label{fig:ex-groups}]
  {\includegraphics[width=.45\linewidth]{figures/example_groups/groups_centered}}
  ~
  \subfloat[Groups after applying convolution and activation operations. \label{fig:ex-groups-after}]{\includegraphics[width=.45\linewidth]{figures/example_groups/groups3d_centered}
  }
  \caption{Exemple of application of convolution with groups centers as filters' weightes.}
  \label{fig:filter}
\end{figure}

>>>>

\begin{figure}[!t]
  \centering
  \subfloat[\label{fig:ex-groups}]
  {\includegraphics[width=.35\linewidth]{figures/example_groups/groups_centered}}
  ~
  \subfloat[\label{fig:ex-groups-after}]{\includegraphics[width=.45\linewidth]{figures/example_groups/groups3d_centered}
  }
  \caption{Exemple of application of convolution with groups centers as filters' weightes: (a) Groups of three classes centered on the origin; (b) Groups after applying convolution and activation operations. }
  \label{fig:filter}
\end{figure}
